%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Amadeus (via Astek)} % Organization
    {(Remote) Antibes, France} % Location
    {Feb. 2020 - Exp. Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to the development of the Search Orchestrator system, aggregating flight offers from multiple airlines.}
        \item {Designed and implemented new features, ensuring software stability through comprehensive tests and proactive maintenance.}
        \item {Improved project architecture and reduced technical debt by proposing and implementing efficient solutions.}
        \item {Advocated for best development practices via knowledge-sharing sessions.}
        \item {Contributed to DevOps efforts, assisting in release and deployment processes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Trainee} % Job title
    {Mentor Graphics (Siemens EDA)} % Organization
    {Montbonnot-Saint-Martin, France} % Location
    {Apr. 2021 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted performance analysis and optimization at the API level to improve data transmission efficiency.}
        \item {Identified and addressed system bottlenecks, enhancing overall performance by up to 20\%.}
        \item {Designed and implemented shared memory communication (POSIX) to optimize interprocess data exchanges.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-Stack Developer} % Job title
    {Reynolds\&Reynolds} % Organization
    {Grenoble, France} % Location
    {Feb. 2018 - Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained a web-based software suite for automotive dealerships.}
        \item {Designed and implemented new features, improving system functionality.}
        \item {Ensured system stability through maintenance and incident resolution.}
        \item {Developed internal tools to streamline and optimize the development process.}
      \end{cvitems}
    }

%---------------------------------------------------------
